---
title: "ML5 Risen & Gilovich Data Preparation"
author: "Contact: Maya Mathur (mmathur@stanford.edu)"
date: "June 4, 2017"
output: pdf_document
---

# Site-Level Data Preparation

Overview: A central script is called to prep each site's data automatically (merging various columns, producing standardized names, and excluding subjects per the a priori attention criterion) while outputting results of sanity checks and producing a within-site interaction plot. The script writes separate files with each site's prepped data. Lastly, all sites' prepped data are stitched into a single analysis dataset.

Plots show standard boxplots (quartiles) with lines overlaying group means. 

```{r, echo=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)

library(plyr)
library(dplyr)
```

## Brigham Young

First manually add the `had.read` and `load` variables:

```{r}
source( "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/3. Analysis/R code/data_prep_functions.R" )

setwd("~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/Brigham Young")
d = read.csv("raw_byu.csv", header=TRUE)

# remove additional header rows
d = d[ -c(1:2), ]

library(plyr)
library(dplyr)

# variable names here are sometimes exactly the same
# rename them to avoid problems
names(d)[ 18: ( length( names(d) ) - 1 ) ] = c( "lkl1", "imp1", "bad1",
                                       "lkl2", "endnum1", "eff.split1", "count.hard1", "count.eff1", "imp2", "bad2",
                                       "lkl3", "endnum2", "eff.split2", "count.hard2", "count.eff2", "imp3", "bad3",
                                       "lkl4", "imp4", "bad4" )

# make had.read variable
d$had.read = NA
d$had.read[ !is.na( as.numeric(as.character( d$lkl1 ) ) ) |
            !is.na( as.numeric(as.character( d$lkl3 ) ) ) ] = 0

d$had.read[ !is.na( as.numeric(as.character( d$lkl2 ) ) ) |
            !is.na( as.numeric(as.character( d$lkl4 ) ) ) ] = 1

# merge end-number columns
# warning about "NAs introduced by coercion", but is correct
d$end.num = coalesce( as.numeric( as.character( d$endnum1 ) ),
                  as.numeric( as.character( d$endnum2 ) ) )

# make load variable based on end-number column
d$load = 0
d$load[ !is.na( as.numeric(as.character( d$end.num ) ) ) ] = 1


# merge effort-split columns
# warning about "NAs introduced by coercion", but is correct
d$eff.split = coalesce( as.numeric( as.character( d$eff.split1 ) ),
                  as.numeric( as.character( d$eff.split2 ) ) )

# merge badness columns
# warning about "NAs introduced by coercion", but is correct
d$badness = coalesce( as.numeric( as.character( d$bad1 ) ),
                  as.numeric( as.character( d$bad2 ) ),
                  as.numeric( as.character( d$bad3 ) ),
                  as.numeric( as.character( d$bad4 ) )
                  )

# merge importance columns
# warning about "NAs introduced by coercion", but is correct
d$importance = coalesce( as.numeric( as.character( d$imp1 ) ),
                  as.numeric( as.character( d$imp2 ) ),
                  as.numeric( as.character( d$imp3 ) ),
                  as.numeric( as.character( d$imp4 ) )
                  )

# merge counting effort columns
# warning about "NAs introduced by coercion", but is correct
d$count.eff = coalesce( as.numeric( as.character( d$count.eff1 ) ),
                  as.numeric( as.character( d$count.eff2 ) )
                  )

# merge counting effort columns
# warning about "NAs introduced by coercion", but is correct
d$count.hard = coalesce( as.numeric( as.character( d$count.hard1 ) ),
                  as.numeric( as.character( d$count.hard2 ) )
                  )

write.csv(d, "manualprep_byu.csv")
```


Automatic data prep:
```{r}
start.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/Brigham Young/manualprep_byu.csv"
end.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Prepped data"

source( "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/3. Analysis/R code/data_prep_functions.R" )
prep_site_data( start.path = start.path, end.path = end.path, 
                      lkl.names = c("lkl1", "lkl2",
                                    "lkl3", "lkl4"),
                      had.read.name = "had.read",
                      load.name = "load",
                      end.num.name = "end.num",
                      eff.split.name = "eff.split",
                      count.eff.name = "count.eff",
                      count.hard.name = "count.hard",
                      badness.name = "badness",
                      importance.name = "importance",
                      .site.name = "BYU", .group = "c.dissimilar",
                      .n.extra.header.rows = 0 )
```



## Eotvos Lorand

First manually exclude 7 subjects who may have completed the experiment twice (note: these 7 are on top of any "bad subjects" excluded by the prep script):
```{r}
source( "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/3. Analysis/R code/data_prep_functions.R" )

setwd("~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/Eotvos Lorand")
d = read.csv("raw_eotvos.csv")

d = d[ !d$ResponseId %in% c( "R_1H76w6p0V7mQW3T", "R_12mU6WnhCkSe5LH", "R_3ReInhemqnhITwd", "R_2tqY0auQ9EUmWCf", "R_Z4tlLy5HCyAXhRf", "R_28BCOFVHOcgVquF",
   "R_1LwH5vC3QBq4uFG" ), ]

write.csv(d, "manualprep_eotvos.csv")
```

Automatic data prep:
```{r}
start.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/Eotvos Lorand/manualprep_eotvos.csv"
end.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Prepped data"

prep_site_data( start.path = start.path, end.path = end.path, 
                      lkl.names = c("L1.R1.scenario_1", "L1.R0.scenario_1",
                                    "L0.R1.text_1", "L0.R0.text_1"),
                      had.read.name = "had.read",
                      load.name = "load",
                      end.num.name = "Q28",
                      eff.split.name = "Q29_1",
                      count.eff.name = "Q22_1",
                      count.hard.name = "Q21_1",
                      badness.name = "Q14_1",
                      importance.name = "Q26_1",
                      .site.name = "Eotvos", .group = "c.dissimilar",
                      .n.extra.header.rows = 2 )
```

## KU Leuven

```{r}
start.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/KU Leuven/raw_kul.csv"
end.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Prepped data"

prep_site_data( start.path = start.path, end.path = end.path, 
                      lkl.names = c("L1.R1.scenario_1", "L1.R0.scenario_1",
                                    "L0.R1.text_1", "L0.R0.text_1"),
                      had.read.name = "had.read",
                      load.name = "load",
                      end.num.name = "Q28",
                      eff.split.name = "Q29_1",
                      count.eff.name = "Q22_1",
                      count.hard.name = "Q21_1",
                      badness.name = "Q14_1",
                      importance.name = "Q26_1",
                      .site.name = "KUL", .group = "c.dissimilar",
                      .n.extra.header.rows = 1 )
```

## PUC Rio


```{r}
start.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/PUC Rio/raw_puc.csv"
end.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Prepped data"

prep_site_data( start.path = start.path, end.path = end.path, 
                      lkl.names = c("L1.R1.scenario_1", "L1.R0.scenario_1",
                                    "L0.R1.text_1", "L0.R0.text_1"),
                      had.read.name = "had.read",
                      load.name = "load",
                      end.num.name = "Q28",
                      eff.split.name = "Q29_1",
                      count.eff.name = "Q22_1",
                      count.hard.name = "Q21_1",
                      badness.name = "Q14_1",
                      importance.name = "Q26_1",
                      .site.name = "PUC", .group = "c.dissimilar",
                      .n.extra.header.rows = 1 )
```



## Rose-Hulman IT

```{r}
start.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/Rose-Hulman IT/raw_rose.csv"
end.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Prepped data"

d = prep_site_data( start.path = start.path, end.path = end.path, 
                      lkl.names = c("likelihood_1", "likelihood_1.1",
                                    "likelihood_1.2", "likelihood_1.3"),
                      had.read.name = "had.read",
                      load.name = "load",
                      end.num.name = "end.num",
                      eff.split.name = "effort.split_1",
                      count.eff.name = "effort.count_1",
                      count.hard.name = "difficulty_1",
                      badness.name = "negativity_1",
                      importance.name = "academic.pressure_1",
                      .site.name = "RHIT", .group = "c.dissimilar",
                      .n.extra.header.rows = 2 )
```

## Stanford

```{r}
start.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/Stanford/raw_stanford.csv"
end.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Prepped data"

prep_site_data( start.path = start.path, end.path = end.path, 
                      lkl.names = c("likelihood_1", "likelihood_1.1",
                                    "likelihood_1.2", "likelihood_1.3"),
                      had.read.name = "had.read",
                      load.name = "load",
                      end.num.name = "end.num",
                      eff.split.name = "effort.split_1",
                      count.eff.name = "effort.count_1",
                      count.hard.name = "difficulty_1",
                      badness.name = "negativity_1",
                      importance.name = "academic.pressure_1",
                      .site.name = "Stanford", .group = "b.similar",
                      .n.extra.header.rows = 2 )
```


## University of Rhode Island

```{r}
start.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/U Rhode Island/raw_uri.csv"
end.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Prepped data"

prep_site_data( start.path = start.path, end.path = end.path, 
                      lkl.names = c("L1.R1.scenario_1", "L1.R0.scenario_1",
                                    "L0.R1.text_1", "L0.R0.text_1"),
                      had.read.name = "had.read",
                      load.name = "load",
                      end.num.name = "Q28",
                      eff.split.name = "Q29_1",
                      count.eff.name = "Q22_1",
                      count.hard.name = "Q21_1",
                      badness.name = "Q14_1",
                      importance.name = "Q26_1",
                      .site.name = "URI", .group = "c.dissimilar",
                      .n.extra.header.rows = 2 )
```

## UC Berkeley

This site used the RPP Qualtrics file instead of the updated ML5 one. The RPP file had exactly the same wording for the main questions but did not have the new "mechanistic" questions; hence all the missing data that the function complains about. 

```{r}
setwd("~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/UC Berkeley")
d = read.csv("raw_ucb.csv", header=TRUE)

# merge end-number columns
# warning about "NAs introduced by coercion", but is correct
d$end.num = coalesce( as.numeric( as.character( d$Q3 ) ),
                  as.numeric( as.character( d$Q8 ) ) )

# merge effort-split columns
# warning about "NAs introduced by coercion", but is correct
d$eff.split = coalesce( as.numeric( as.character( d$Q4_1 ) ),
                  as.numeric( as.character( d$Q9_1 ) ) )

# placeholders for vars not collected
d$badness = NA
d$importance = NA
d$count.eff = NA
d$count.hard = NA
  
write.csv(d, "manualprep_ucb.csv")
```


Automatic prep:
```{r}
start.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/UC Berkeley/manualprep_ucb.csv"
end.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Prepped data"

prep_site_data( start.path = start.path, end.path = end.path, 
                      lkl.names = c("Q2_1", "Q7_1",
                                    "Q11_1", "Q14_1"),
                      had.read.name = "Had.read",
                      load.name = "Cognitive.load",
                      end.num.name = "end.num",
                      eff.split.name = "eff.split",
                      count.eff.name = "count.eff",
                      count.hard.name = "count.hard",
                      badness.name = "badness",
                      importance.name = "badness",
                      .site.name = "UCB", .group = "b.similar",
                      .n.extra.header.rows = 1 )
```


## University of Pennsylvania

```{r}
start.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/UPenn/raw_upenn.csv"
end.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Prepped data"

prep_site_data( start.path = start.path, end.path = end.path, 
                      lkl.names = c("L1.R1.scenario_1", "L1.R0.scenario_1",
                                    "L0.R1.text_1", "L0.R0.text_1"),
                      had.read.name = "had.read",
                      load.name = "load",
                      end.num.name = "Q28",
                      eff.split.name = "Q29_1",
                      count.eff.name = "Q22_1",
                      count.hard.name = "Q21_1",
                      badness.name = "Q14_1",
                      importance.name = "Q26_1",
                      .site.name = "U Penn", .group = "b.similar",
                      .n.extra.header.rows = 2 )
```



## Mechanical Turk 

```{r}
start.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/MTurk/raw_mturk.csv"
end.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Prepped data"

prep_site_data( start.path = start.path, end.path = end.path, 
                      lkl.names = c("L1.R1.scenario_1", "L1.R0.scenario_1",
                                    "L0.R1.text_1", "L0.R0.text_1"),
                      had.read.name = "had.read",
                      load.name = "load",
                      end.num.name = "Q28",
                      eff.split.name = "Q29_1",
                      count.eff.name = "Q22_1",
                      count.hard.name = "Q21_1",
                      badness.name = "Q14_1",
                      importance.name = "Q26_1",
                      .site.name = "MTurk", .group = "a.mturk",
                      .n.extra.header.rows = 2 )
```




## University of Virginia (UVA)

```{r}
start.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Raw data/U Virginia/raw_uva.csv"
end.path = "~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Prepped data"

d = prep_site_data( start.path = start.path, end.path = end.path, 
                      lkl.names = c("likelihood_1", "likelihood_1.1",
                                    "likelihood_1.2", "likelihood_1.3"),
                      had.read.name = "had.read",
                      load.name = "load",
                      end.num.name = "end.num",
                      eff.split.name = "effort.split_1",
                      count.eff.name = "effort.count_1",
                      count.hard.name = "difficulty_1",
                      badness.name = "negativity_1",
                      importance.name = "academic.pressure_1",
                      .site.name = "UVA", .group = "b.similar",
                      .n.extra.header.rows = 2 )
```





# Aggregated Data Preparation

Stitch datasets:
```{r}
setwd("~/Dropbox/Personal computer/Independent studies/Many Labs 5 (ML5)/Linked to OSF/2. Data/Prepped data")

# if there is already prepped data from a previous run, remove it
#  to avoid attempting to rbind it with site data
if ( "prepped_data.csv" %in% list.files() ) file.remove("prepped_data.csv")

# rbind all the datasets into one
b = do.call( "rbind", lapply( list.files(), function(x) read.csv(x, header=TRUE ) ) )

# rename a few cols
names(b)[ names(b) == ".site.name" ] = "site"
names(b)[ names(b) == ".group" ] = "group"

# add a few cols
b$is.mturk = 0
b$is.mturk[ b$group=="a.mturk" ] = 1

# write data
write.csv(b, "prepped_data.csv")
```

